Space-time adaptivity for parabolic evolution equations

### 2020-05-15 Latex/pint2020-westerdiep.tex
first pass latex

Taking the well-posed mixed simultaneous space-time variational formulation
introduced in~\cite{And13}, we use methods previously developed in~\cite{SW20}
to construct an adaptive loop that produces space-time approximations as linear
combinations of tensor-products of wavelets in time and finite elements in space.

Using an efficient and reliable `hierarchical basis' error estimator, we apply bulk
chasing to show convergence of the iterands. Moreover, we provide an algorithm for
linear-complexity application of the system matrix and an optimal preconditioner.
Lastly, we include an extensive numerical study to show that this method is competitive
in terms of speed and moreover exhibits optimal convergence rate in the number of
degrees of freedom.

>>>>

Taking the well-posed mixed simultaneous space-time variational formulation
introduced in~\cite{And13}, we use methods previously developed in~\cite{SW20}
to construct an adaptive refinement loop that produces nested space-time
approximations as linear combinations of tensor-products of wavelets in time and
finite elements in space.

The sequence of approximations produced by this loop exhibits optimal convergence
rate in the number of degrees of freedom, at an optimal computational cost. The
result is that for certain problems, large-scale parallel space-time solvers may
be unnecessary and can be replaced by a method that adapts itself to the problem.
